Weak gravitational lensing shear \textcolor{red}{estimation} with \textsc{metacalibration} for the \emph{Roman} High-Latitude Imaging Survey

### 2022-03-11 paper_v3.tex
rachel's comments v4.1

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\normalem
\title[Metacalibration for the Roman High-Latitude Imaging Survey]{Weak gravitational lensing shear estimates with \textsc{metacalibration} for the \emph{Roman} High-Latitude Imaging Survey}

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[M. Yamamoto et al.]{
Masaya Yamamoto,$^{1}$\thanks{E-mail: masaya.yamamoto@duke.edu}
M. A. Troxel,$^{1}$
Mike Jarvis,$^{2}$
Rachel Mandelbaum,$^{3}$
Christopher Hirata,$^{4,5,6}$
 et al.\\
% List of institutions
$^{1}$Department of Physics, Duke University, Durham, NC, 27710\\
$^{2}$Department of Physics and Astronomy, University of Pennsylvania, Philadelphia, PA 19104, USA\\
$^{3}$McWilliams Center for Cosmology, Department of Physics, Carnegie Mellon University, Pittsburgh, Pennsylvania 15213, USA\\
$^{4}$Center for Cosmology and Astro-Particle Physics, The Ohio State University, 191 West Woodruff Avenue, Columbus, OH 43210, USA\\
$^{5}$Department of Physics, The Ohio State University, 191 West Woodruff Avenue, Columbus, OH 43210, USA\\
$^{6}$Department of Astronomy, The Ohio State University, 140 West 18th Avenue, Columbus, OH 43210, USA\\
}

@@

% Abstract of the paper
\begin{abstract}
We investigate the performance of the \textsc{metacalibration} shear calibration framework using simulated imaging data for the \emph{Nancy Grace Roman} Space Telescope (\emph{Roman}) reference High-Latitude Imaging Survey (HLIS). 
%These large-scale realistic image simulations are necessary to measure shear bias to confirm that the requirements of the instrument and the overall weak lensing survey strategy are met. 
The weak lensing program of the \emph{Roman} mission requires the mean galaxy ellipticity to be calibrated within about 0.03\%. To reach this goal, we can test our calibration process with various simulations and ultimately isolate the sources where these residual shear biases might arise in order to improve our methods. In this work, we build on the first set of Roman HLIS simulated imaging data in \cite{2021MNRAS.501.2044T} to incorporate several new realistic processing-pipeline updates necessary to more accurately process the imaging data and calibrate the shear. We show the first results of this calibration for six deg$^{2}$ of the simulated reference HLIS using \textsc{metacalibration} and compare these results to measurements on more simple, faster Roman-like image simulations. In both cases, we neglect the impact of blending of objects. We find that in the simplified simulations, \textsc{metacalibration} can calibrate shapes to within $m=(-0.01\pm 0.10)$\%. When applied to the current most-realistic version of the simulations, the precision is much lower, with a \textsc{metacalibration} estimate of $m=(-1.34\pm 0.67)$\% for joint multi-band single-epoch measurements and $m=(-1.13\pm 0.60)$\% for multi-band coadd measurements. These results are all consistent with zero within 1--2$\sigma$, indicating we are currently limited by our simulated survey volume. Further work on testing the shear calibration methodology is necessary at higher precision to reach the levels of the \textit{Roman} requirements, in particular in the presence of blending. 
%In the future, we will need to substantially increase the simulation volume by $\sim$400 (about the same size as the survey area of 2000 deg$^{2}$) to reach the precision necessary to test the HLIS requirements. 
Current results demonstrate, however, that the \textsc{metacalibration} method can work on undersampled space-based imaging data at well-below the requirements levels of current weak lensing surveys.
\end{abstract}

@@

Since the formulation of a physical cosmological model, observational evidence has shown that the contents of the universe are mostly in the dark sector (\citealt{2020A&A...641A...8P, 2020MNRAS.498.2492G, 2020MNRAS.499.5527T, 2021A&A...645A.104A, 2022PhRvD.105b3520A, 2022arXiv220204077B}). Within this sector, dark energy accounts for the accelerating expansion of the universe (e.g., \citealt{1998AJ....116.1009R, 1999AIPC..478..129P}) and the combination of dark energy and dark matter are responsible for the observed growth of large-scale structure (\citealt{2015RPPh...78h6901K, 2017grle.book.....D}). The growth can be studied by carefully reconstructing the paths of the light leaving distant galaxies and going through the regions where mass concentrates in the universe; this physical phenomenon is called gravitational lensing. “Weak” gravitational lensing causes a slight distortion to intrinsic galaxy shapes called shear. By detecting millions of these gravitationally lensed galaxies and computing their ensemble shear, we can explore the dark matter density and the amplitude of matter fluctuation in the universe (e.g., \citealt{2001PhR...340..291B}). Measuring these quantities eventually helps us learn about the history of the development of the large-scale structure in the universe. For that reason, weak lensing is one of the most powerful probes in current and near-future imaging surveys to constrain cosmological parameters with high precision.

Due to the subtlety in the lensing effect and its systematics-dominant nature in the weak regime, observational efforts have been challenging. Over the past decade, large international collaborations such as the Dark Energy Survey\footnote{\url{http://www.darkenergysurvey.org/}} (DES: \citealt{2005astro.ph.10346T}), the Hyper Supreme-Cam\footnote{\url{http://hsc.mtk.nao.ac.jp/ssp/}} (HSC: \citealt{2018PASJ...70S...4A}), and the Kilo-Degree Survey\footnote{\url{http://kids.strw.leidenuniv.nl/}} (KiDS: \citealt{2013ExA....35...25D}) have been successful at constraining the cosmological parameters, and the precision in calibrating the shapes of distant galaxies has reached a few percent (\citealt{2020arXiv201103408G, 2020arXiv201208567M, 2021A&A...645A.105G}). As we observe more area of the sky and develop better tools (observatories and algorithms), we detect more galaxies, and have already reached the point where statistical and systematic uncertainties are comparable. Thus, near-future Stage IV surveys (\citealt{2006astro.ph..9591A}) such as Euclid\footnote{\url{ http://sci.esa.int/euclid}} (\citealt{2011arXiv1110.3193L}), the Vera C. Rubin Observatory Legacy Survey of Space and Time\footnote{\url{ http://www.lsst.org}} (\emph{Rubin}: \citealt{2009arXiv0912.0201L, 2019ApJ...873..111I}), and the \emph{Nancy Grace Roman} Space Telescope\footnote{\url{https://roman.gsfc.nasa.gov}} (\emph{Roman}: \citealt{2015arXiv150303757S}) require even better control of systematics. In order to understand the systematic uncertainties we face, we must develop realistic image simulations, apply existing shape measurement methods to the simulated images, and determine any potential residual systematic effects and build a strategy for modifying the calibration methodology to mitigate them.

Based on our current knowledge, systematic biases for weak lensing science, both observational and astrophysical, can occur at all stages of the imaging survey (e.g., \citealt{2018ARA&A..56..393M}). Particularly, observational systematics can be due to: 
\begin{itemize}
    \item inhomogeneous observing strategy,
    \item instrumentation effects,
    \item post-processing pipelines such as image coaddition and object detection.
\end{itemize} 
Conventionally, these observational systematic biases are characterized through a number of simulations and validation tests, and these propagate into uncertainties on the final mean galaxy shear we measure. We quantify this impact as shear calibration bias. There have been several shear calibration and bias mitigation efforts that were proposed by the STEP (\citealt{2006MNRAS.368.1323H, 2007MNRAS.376...13M}) and GREAT (\citealt{2010MNRAS.405.2044B, 2013ApJS..205...12K, 2015MNRAS.450.2963M}) challenges, to meet the requirements for the current imaging surveys. In particular, one of the state-of-the-art self-calibration methods, \textsc{metacalibration} (\citealt{2017arXiv170202600H, 2017ApJ...841...24S}) has been shown to be able to substantially reduce the significance of shear bias. It has been confirmed that shear can be calibrated with \textsc{metacalibration} at the few-percent level in DES (\citealt{2018MNRAS.481.1149Z, 2020arXiv201103408G}), without accounting for galaxy blending and detection. Tackling the issue of blending/detection is one key step forward for the DES Y6 analysis and preparatory Rubin LSST work with the shear-dependent detection and calibration technique \textsc{metadetection} (\citealt{2020ApJ...902..138S}). While the major advantage of \textsc{metacalibration} or \textsc{metadetection} is that they can be directly applied to real galaxy images without needing to rely on an ensemble calibration from image simulations, limitations for future surveys are not well-known.

One possible limitation might lie in the effect of undersampled images in space-based surveys like \emph{Euclid} and \emph{Roman}, which will operate at its diffraction-limit. The PSF needs to be interpolated and estimated from well-sampled images to accurately deconvolve and measure shapes with, because the \emph{Roman} PSF has a complex structure that cannot be captured in the original undersampled images. It is, therefore, necessary to build a robust strategy to reconstruct well-sampled images to estimate the PSF to allow unbiased shape measurement.
Recently, \cite{2021MNRAS.502.4048K} (hereafter K21) addressed this potential issue of the limitations of \textsc{metacalibration} on undersampled images in \emph{Euclid} image simulations. They found that for the \emph{Euclid} mission the shear estimate with \textsc{metacalibration} is biased by about 1$\%$. It is mentioned that their result could be extended to the \emph{Roman} mission due to similarities in the instruments and for \emph{Roman} they predicted the multiplicative bias was more than 1\%. They show that these effects can be mitigated using additional weighting kernels in the measurement.

In this work, we explore how \textsc{metacalibration} performs using coadd images at higher resolution, taking advantage of the dithering of images in the reference HLIS. We use an updated suite of image simulations specifically made for the \emph{Roman} reference HLIS mission. Our work is based on the image simulation suite for the \emph{Roman} Space Telescope developed by \cite{2021MNRAS.501.2044T} (hereafter T21), where we render star and galaxy images using \texttt{GalSim}\footnote{\url{ https://github.com/GalSim-developers/GalSim}} (\citealt{2015A&C....10..121R}). We describe several important updates to the simulation capabilities and realism following T21. We also implement for the first time \textsc{metacalibration} using the simulated imaging, so that we can start to explore if the shear calibration goals of the HLIS for \emph{Roman} ($m=~3.2\times10^{-4}$) (\citealt{2018arXiv180403628D}) can be achieved with current \textsc{metacalibration} pipelines,\footnote{We limit the study to \textsc{metacalibration} for now, since we can extract unblended cutouts of objects in our simulations.} or will require substantial additional development. \par

@@

\section{Background}
\label{sec:background}
In this section, we provide a brief introduction of image sampling defined through the Nyquist-Shannon Sampling Theorem, an overview of shear calibration bias within the context of weak lensing, and the \textsc{metacalibration} formalism.

\subsection{Image Sampling}
Based on the Nyquist-Shannon Sampling Theorem which states that in order to reconstruct an unbiased continuous band-limited function without a loss of information, the sufficient sample rate is twice the bandlimiting frequency per second. In the context of image sampling, the criterion that the sample pixel spacing needs to satisfy is $p < \frac{1}{2u_{max}}$ ($u_{max}$ is the max. spatial bandlimiting frequency). Since the spatial bandlimiting frequency in an astronomical image is defined as, 
\begin{equation}
    u_{max} = \frac{1}{\lambda_{min}N_{f}}
\end{equation}
the sampling factor of the \emph{Roman} images is defined as, 
\begin{equation}
    Q = \frac{\lambda_{min}N_{f}}{p}, 
    \label{eqn:sampling}
\end{equation}
where $\lambda_{min}$ is the shortest wavelength of the incident light in each filter, $N_{f}$ is the focal ratio of the telescope ($N_{f}=7.8$ for \emph{Roman}) and $p$ is the pixel spacing of the sensor ($p=10\mu m$ for \emph{Roman}) (\citealt{2013PASP..125.1496S}). An image with sampling factor $Q=2$ is considered Nyquist-sampled and an image with with sampling factor $Q<2$ is undersampled.

@@

\subsection{Shear Calibration Bias}
In the observation of cosmic shear, we can quantify the bias associated with the shear recovery processes such as PSF estimation and shape measurement in image simulations. We call this shear calibration bias and we compute the deviations of the measured gravitational lensing shear $\gamma$ from the input shear. In the limit of weak lensing ($\lvert\gamma\rvert\ll1$) and random intrinsic galaxy shapes, the ensemble average of ellipticities $\langle e \rangle$ of galaxy shapes is directly related to the reduced shear field $g$, and the estimated shear can be written as a linear model with multiplicative ($m_{i}$) and additive bias ($c_{i}$) as described in the equation below (\citealt{2006MNRAS.368.1323H, 2006MNRAS.366..101H, 2007MNRAS.376...13M}) 
\begin{equation}
    g^{obs}_{i} = (1+m_{i})g^{true}_{i} + c_{i}, 
    \label{eqn:linear}
\end{equation}
where i=(1,2) and $g^{obs}_{i}$ is the two-component observed reduced shear after calibrations and $g^{true}_{i}$ is the true shear. The bias can be introduced in places such as PSF modeling, blending, and the undersampling of the image (e.g., \citealt{2018ARA&A..56..393M}). Additionally, complex detector effects such as the brighter-fatter effect are potential sources of bias (\citealt{2013MNRAS.429..661M}), while it has been shown that for \emph{Roman} the effect of persistence will not be an issue (\citealt{2021arXiv210610273L}). Qualitatively, if the recovered shear is biased by 1$\%$ ($m=0.01$), $S_{8} = \sigma_{8} \sqrt{\Omega_{m}/0.3}$ could be biased about 1.5$\%$ in the final cosmology result. Thus, quantifying and correcting these biases before the real survey begins is extremely important.

\begin{figure}
	\includegraphics[width=\columnwidth]{metacal_bias_shear.pdf}
    %\vspace*{-5mm}
    \caption{We show the recovered multiplicative bias on the shear as a function of applied shear for the choice of the applied shear in our simulations. The presented multiplicative bias is the average of $m_{1}$ and $m_{2}$. At first order, the \textsc{metacalibration} algorithm only works for small input shears. The next order effect is seen as a quadratic dependence of the multiplicative shear bias on on the applied shear (\citealt{2017ApJ...841...24S}). A larger input shear increases the signal-to-noise of bias estimates, but to keep the non-linear effect small compared to requirements, we limit input shears to $\pm 0.02$. }
    \label{fig:metacal_shear_linear}
\end{figure}

\subsection{\textsc{metacalibration} Formalism}
Here, we describe the general features of how \textsc{metacalibration} calibrates the biased measurement of galaxy ellipticities on the image stamps. \textsc{metacalibration} creates one unsheared and four artificially-sheared galaxy stamps. Each is deconvolved with the input PSF, left unsheared or sheared with an additional gravitational shear of $\delta\gamma=\pm 0.01$ in the two basis directions ($+g1$, $-g1$, $+g2$, $-g2$) and re-convolved with a new slightly larger isotropic, Gaussian PSF. \textsc{metacalibration} works under the assumption that the input shear is small, otherwise the recovered shear would be biased without accounting for higher order terms. It is a balance to choose an input shear that results in higher S/N of an object and unbiased shape measurement. Figure \ref{fig:metacal_shear_linear} shows the performance as a function of input shear leading to the choice of input shear $\gamma=\pm 0.02$.

After processing the images in \textsc{metacalibration} and measuring the shapes in \texttt{ngmix}, we have 5 shape catalogs in each \textsc{metacalibration} shear direction. We can then compute the shear response from these catalogs and calculate the calibrated ensemble galaxy ellipticities. The shear response can be understood as the change in objects' ellipticities with respect to the change in gravitational shear. Mathematically, the observed ellipticities, $\vb*{e}$ = ($e_{1}$, $e_{2}$), can be approximated using a Taylor expansion around the two-component shear, $\vb*{\gamma}=0$. Higher terms here can be dropped assuming the gravitational shear is small (reduced shear). 
\begin{equation}
    \vb*{e} = \vb*{e}\rvert_{\vb*{\gamma}=0} + \frac{\partial \vb*{e}}{\partial \vb*{\gamma}}\bigg\rvert_{\vb*{\gamma}=0}\vb*{\gamma} + \ldots
\end{equation}
From this expression, the shear response matrix can be defined as, 
\begin{equation}
    \vb*{R} \equiv \frac{\partial \vb*{e}}{\partial \vb*{\gamma}}\bigg\rvert_{\vb*{\gamma}=0} = 
    \begin{pmatrix}
        \partial e_{1}/\partial \gamma_{1} & \partial e_{2}/\partial \gamma_{1} \\ 
        \partial e_{1}/\partial \gamma_{2} & \partial e_{2}/\partial \gamma_{2}
    \end{pmatrix}. 
\end{equation}
The ensemble mean of measured ellipticities $\langle\vb*{e}\rangle$ can then computed. Since we expect galaxies to be randomly oriented such that $\langle\vb*{e}\rangle\rvert_{\vb*{\gamma}=0}=0$, we have a relationship between the measured ellipticities and the input shear in the simulations, 
\begin{equation}
    \langle\vb*{e}\rangle \approx \langle \vb*{R}\rangle\langle\vb*{\gamma} \rangle. 
\end{equation}

In practice, we compute the mean shear response from the five versions of \textsc{metacalibration} catalog using the finite difference method.

\begin{equation}
    \langle\vb*{R_{ij}}\rangle = 
    \frac{\langle e^{+}_{i} - e^{-}_{i} \rangle}{\delta\gamma_{j}}, 
\end{equation}
where $e^{+}_{i}$ and $e^{-}_{i}$ is the $i$-th component of the galaxy ellipticity where positive ($+$) or negative ($-$) shear is applied in $i$-th direction.

>>>>

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\normalem
\title[Metacalibration for the Roman High-Latitude Imaging Survey]{Weak gravitational lensing shear \textcolor{red}{estimation} with \textsc{metacalibration} for the \emph{Roman} High-Latitude Imaging Survey}

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[M. Yamamoto et al.]{
Masaya Yamamoto,$^{1}$\thanks{E-mail: masaya.yamamoto@duke.edu}
M. A. Troxel,$^{1}$
Mike Jarvis,$^{2}$
Rachel Mandelbaum,$^{3}$
Christopher Hirata,$^{4,5,6}$
\newauthor{
Ami Choi,$^{7}$
Tianqing Zhang,$^{3}$}\\
% List of institutions
$^{1}$Department of Physics, Duke University, Durham, NC, 27710\\
$^{2}$Department of Physics and Astronomy, University of Pennsylvania, Philadelphia, PA 19104, USA\\
$^{3}$McWilliams Center for Cosmology, Department of Physics, Carnegie Mellon University, Pittsburgh, Pennsylvania 15213, USA\\
$^{4}$Center for Cosmology and Astro-Particle Physics, The Ohio State University, 191 West Woodruff Avenue, Columbus, OH 43210, USA\\
$^{5}$Department of Physics, The Ohio State University, 191 West Woodruff Avenue, Columbus, OH 43210, USA\\
$^{6}$Department of Astronomy, The Ohio State University, 140 West 18th Avenue, Columbus, OH 43210, USA\\
$^{7}$Department of Physics, California Institute of Technology, 1200 E. California Blvd., Pasadena, California 91125, USA\\
}

@@

% Abstract of the paper
\begin{abstract}
We investigate the performance of the \textsc{metacalibration} shear calibration framework using simulated imaging data for the \emph{Nancy Grace Roman} Space Telescope (\emph{Roman}) reference High-Latitude Imaging Survey (HLIS). 
%These large-scale realistic image simulations are necessary to measure shear bias to confirm that the requirements of the instrument and the overall weak lensing survey strategy are met. 
The weak lensing program of the \emph{Roman} mission requires the mean weak lensing shear estimate to be calibrated within about 0.03\%. To reach this goal, we can test our calibration process with various simulations and ultimately isolate the sources of residual shear biases in order to improve our methods. In this work, we build on the Roman HLIS image simulation pipeline in \cite{2021MNRAS.501.2044T} to incorporate several new realistic processing-pipeline updates necessary to more accurately process the imaging data and calibrate the shear. We show the first results of this calibration for six \textrm{deg}$^{2}$ of the simulated reference HLIS using \textsc{metacalibration} and compare these results to measurements on more simple, faster Roman-like image simulations. In both cases, we neglect the impact of blending of objects. We find that in the simplified simulations, \textsc{metacalibration} can calibrate shapes to within $m=(-0.01\pm 0.10)$\%. When applied to the current most-realistic version of the simulations, the precision is much lower, with a \textsc{metacalibration} estimate of $m=(-1.34\pm 0.67)$\% for joint multi-band single-epoch measurements and $m=(-1.13\pm 0.60)$\% for multi-band coadd measurements. These results are all consistent with zero within 1--2$\sigma$, indicating we are currently limited by our simulated survey volume. Further work on testing the shear calibration methodology is necessary at higher precision to reach the levels of the \textit{Roman} requirements, in particular in the presence of blending. 
%In the future, we will need to substantially increase the simulation volume by $\sim$400 (about the same size as the survey area of 2000 deg$^{2}$) to reach the precision necessary to test the HLIS requirements. 
Current results demonstrate, however, that the \textsc{metacalibration} method can work on undersampled space-based imaging data at the levels comparable to the requirements levels of current weak lensing surveys.
\end{abstract}

@@

Since the formulation of the standard cosmological model, most observational evidence has been consistent with the flat $\Lambda$-CDM model in which the contents of the universe are mostly in the dark sector (\citealt{2020A&A...641A...8P, 2020MNRAS.498.2492G, 2020MNRAS.499.5527T, 2021A&A...645A.104A, 2022PhRvD.105b3520A, 2022arXiv220204077B}). Within this sector, dark energy accounts for the accelerating expansion of the universe (e.g., \citealt{1998AJ....116.1009R, 1999AIPC..478..129P}) and the combination of dark energy and dark matter are responsible for the observed growth of large-scale structure (\citealt{2015RPPh...78h6901K, 2017grle.book.....D}). \textcolor{red}{The growth can be studied by measuring quantities that are sensitive to the way light rays are deflected by intervening mass in the Universe, a physical phenomenon called gravitational lensing.} “Weak” gravitational lensing causes a slight distortion to intrinsic galaxy shapes called shear. By detecting millions of these gravitationally lensed galaxies and computing their ensemble shear, we can explore the dark matter density and the amplitude of matter fluctuation in the universe (e.g., \citealt{2001PhR...340..291B}). Measuring these quantities eventually helps us learn about the history of the development of the large-scale structure in the universe. For that reason, weak lensing is one of the most powerful probes in current and near-future imaging surveys to constrain cosmological parameters with high precision.

Due to the subtlety in the lensing effect and its systematics-dominant nature in the weak regime (\citealt{2018ARA&A..56..393M}), observational efforts have been challenging. Over the past decade, large international collaborations such as the Dark Energy Survey\footnote{\url{http://www.darkenergysurvey.org/}} (DES: \citealt{2005astro.ph.10346T}), the Hyper Suprime-Cam Subaru Strategic Program\footnote{\url{http://hsc.mtk.nao.ac.jp/ssp/}} (HSC: \citealt{2018PASJ...70S...4A}), and the Kilo-Degree Survey\footnote{\url{http://kids.strw.leidenuniv.nl/}} (KiDS: \citealt{2013ExA....35...25D}) have been successful at constraining the cosmological parameters, and the precision in calibrating the estimates of shear from the shapes of distant galaxies has reached a few percent (\citealt{2018MNRAS.481.3170M, 2020arXiv201103408G, 2020arXiv201208567M, 2021A&A...645A.105G}). As we observe more area on the sky and develop better tools (observatories and algorithms), we detect more galaxies, and have already reached the point where statistical and systematic uncertainties are comparable. Thus, near-future Stage IV surveys (\citealt{2006astro.ph..9591A}) such as Euclid\footnote{\url{ http://sci.esa.int/euclid}} (\citealt{2011arXiv1110.3193L}), the Vera C. Rubin Observatory Legacy Survey of Space and Time\footnote{\url{ http://www.lsst.org}} (\emph{LSST}: \citealt{2009arXiv0912.0201L, 2019ApJ...873..111I}), and the \emph{Nancy Grace Roman} Space Telescope\footnote{\url{https://roman.gsfc.nasa.gov}} (\emph{Roman}: \citealt{2015arXiv150303757S}) require even better control of systematics. In order to understand the systematic uncertainties we face, we must develop realistic image simulations, apply existing shape measurement methods to the simulated images, and determine any potential residual systematic effects and build a strategy for modifying the calibration methodology to mitigate them.

Based on our current knowledge, systematic biases for weak lensing science, both observational and astrophysical, can occur at all stages of the imaging survey (e.g., \citealt{2018ARA&A..56..393M}). In particular, observational systematics can be due to: 
\begin{itemize}
    \item inhomogeneous observing strategy,
    \item \textcolor{red}{atmospheric and} instrumentation effects,
    \item post-processing pipelines such as image coaddition and object detection.
\end{itemize} 
Conventionally, these observational systematic biases are characterized through a number of simulations and validation tests, and these propagate into uncertainties on the final mean galaxy shear we measure. We quantify this impact as shear calibration bias. Several shear calibration and bias mitigation efforts have been inspired by the outcomes of the Shear TEsting Programme (STEP; \citealt{2006MNRAS.368.1323H, 2007MNRAS.376...13M}), the GRavitational lEnsing Accuracy Testing challenges (GREAT; \citealt{2010MNRAS.405.2044B, 2013ApJS..205...12K, 2015MNRAS.450.2963M}) \textcolor{red}{and other image simulations work (e.g., \citealt{2017MNRAS.468.3295H})}, to meet the requirements for the current imaging surveys. In particular, one of the state-of-the-art self-calibration methods, \textsc{metacalibration} (\citealt{2017arXiv170202600H, 2017ApJ...841...24S}) has been shown to be able to substantially reduce the significance of shear bias. It has been confirmed that shear can be calibrated with \textsc{metacalibration} at the few-percent level in DES (\citealt{2018MNRAS.481.1149Z, 2020arXiv201103408G}), without accounting for galaxy blending and detection. Tackling the issue of blending/detection is one key step forward for the DES Y6 analysis and preparatory Rubin LSST work with the shear-dependent detection and calibration technique \textsc{metadetection}\footnote{\textcolor{red}{\textsc{metadetection} reduces a significant amount of shear-dependent detection bias by shearing a small region of the sky and applying detection.} } (\citealt{2020ApJ...902..138S}). While the major advantage of \textsc{metacalibration} or \textsc{metadetection} is that they can be directly applied to real galaxy images without needing to rely on an ensemble calibration from image simulations, limitations for future surveys are not well-known.

One possible limitation might lie in the effect of undersampled images in space-based surveys like \emph{Euclid} and \emph{Roman}, which will operate at \textcolor{red}{their respective diffraction limits}. The \textcolor{red}{Point Spread Function (PSF)} needs to be interpolated and estimated from well-sampled images to accurately deconvolve and measure shapes with, because the \emph{Roman} PSF has a complex structure that cannot be captured in the original undersampled images. It is, therefore, necessary to build a robust strategy to reconstruct well-sampled images to estimate the PSF to allow unbiased shape measurement.
Recently, \cite{2021MNRAS.502.4048K} (hereafter K21) addressed this potential issue of the limitations of \textsc{metacalibration} on undersampled images in \emph{Euclid} image simulations. They found that for the \emph{Euclid} mission the shear estimate with \textsc{metacalibration} is biased by about 1$\%$. It is mentioned that their result could be extended to the \emph{Roman} mission due to similarities in the instruments and for \emph{Roman} they predicted the multiplicative bias was more than 1\%. They show that these effects can be mitigated using additional weighting kernels in the measurement.

In this work, we explore how \textsc{metacalibration} performs using coadd images at higher resolution than the native resolution of the instrument, taking advantage of the dithering of images in the reference HLIS. We use an updated suite of image simulations specifically made for the \emph{Roman} reference HLIS mission. Our work is based on the image simulation suite for the \emph{Roman} Space Telescope developed by \cite{2021MNRAS.501.2044T} (hereafter T21), where we render star and galaxy images using \texttt{GalSim}\footnote{\url{ https://github.com/GalSim-developers/GalSim}} (\citealt{2015A&C....10..121R}). We describe several important updates to the simulation capabilities and realism following T21. We also implement for the first time \textsc{metacalibration} using the simulated imaging within the T21 simulation suite, so that we can start to explore if the shear calibration goals of the HLIS for \emph{Roman} ($m=~3.2\times10^{-4}$) (\citealt{2018arXiv180403628D}) can be achieved with current \textsc{metacalibration} implementations,\footnote{We limit the study to \textsc{metacalibration} for now, since we can extract unblended cutouts of objects in our simulations.} or will require substantial additional development. \par

@@

\section{Background}
\label{sec:background}
In this section, we provide a brief introduction to image sampling defined through the Nyquist-Shannon Sampling Theorem, an overview of shear calibration bias within the context of weak lensing, and the \textsc{metacalibration} formalism.

\subsection{Image Sampling}
Based on the Nyquist-Shannon Sampling Theorem, which states that in order to reconstruct an unbiased continuous band-limited function without a loss of information, the sufficient sample rate is twice the bandlimiting frequency per second. In the context of image sampling, the criterion that the sample pixel spacing needs to satisfy is $p < \frac{1}{2u_{\text{max}}}$ ($u_{\text{max}}$ is the maximum spatial bandlimiting frequency). \textcolor{red}{The angular resolution of the diffraction-limited system is $\theta = \lambda/D$ (D: the diameter of an effective aperture) and .} Since the spatial bandlimiting frequency in an astronomical image is defined as 
\begin{equation}
    u_{max} = \frac{1}{\lambda_{\text{min}}N_{f}}
\end{equation}
the sampling factor for \textcolor{red}{a space telescope} is defined as 
\begin{equation}
    Q = \frac{\lambda_{\text{min}}N_{f}}{p}, 
    \label{eqn:sampling}
\end{equation}
where $\lambda_{\text{min}}$ is the shortest wavelength of the incident light in each filter, $N_{f}$ is the focal ratio of the telescope ($N_{f}=7.8$ for \emph{Roman}) and $p$ is the pixel spacing of the sensor ($p=10\,\mu m$ for \emph{Roman}) (\citealt{2013PASP..125.1496S}). An image with sampling factor $Q=2$ is considered Nyquist-sampled and an image with sampling factor $Q<2$ is undersampled. \textcolor{red}{The image samplings for \emph{Roman} are $Q$=0.88, 1.08, 1.31 for J129, H158, and F184 bandpasses respectively. }

@@

\subsection{Shear Calibration Bias}
In the observation of weak lensing, we can quantify the bias associated with the shear recovery processes such as PSF estimation and shape measurement in image simulations. We call this shear calibration bias and we compute the deviations of the measured gravitational lensing shear $\gamma$ from the input shear. \textcolor{red}{Here we define the reduced shear $g \equiv \gamma/(1-\kappa)$, and it is safe to approximate $\gamma \approx g$ in the context of cosmic shear.} In the limit of weak lensing ($\lvert\gamma\rvert\ll1$, $\lvert\kappa\rvert\ll1$) and random intrinsic galaxy shapes, the ensemble average of ellipticities $\langle e \rangle$ of galaxy shapes is directly related to the reduced shear field $g$, and the estimated shear can be written as a linear model with multiplicative ($m_{i}$) and additive bias ($c_{i}$) as described in the equation below (\citealt{2006MNRAS.368.1323H, 2006MNRAS.366..101H, 2007MNRAS.376...13M}) 
\begin{equation}
    g^{\textrm{obs}}_{i} = (1+m_{i})g^{\textrm{true}}_{i} + c_{i}, 
    \label{eqn:linear}
\end{equation}
where $i$=(1,2) \textcolor{red}{due to the rotational symmetry of an ellipse} and $g^{\textrm{obs}}_{i}$ is the two-component observed reduced shear after calibrations and $g^{\textrm{true}}_{i}$ is the true shear. The bias can be introduced in places such as PSF modeling, blending, and the undersampling of the image (e.g., \citealt{2018ARA&A..56..393M}). Additionally, complex detector effects such as the brighter-fatter effect are potential sources of bias (\citealt{2020PASP..132a4502C}), while it has been shown that for \emph{Roman} the effect of persistence will not be an issue (\citealt{2021arXiv210610273L}). Qualitatively, if the recovered shear is biased by 1$\%$ ($m=0.01$), \textcolor{red}{from the cosmic shear power spectrum $S_{8} = \sigma_{8} \sqrt{\Omega_{m}/0.3}$ could be estimated to be biased} about 1.5$\%$ in the final cosmology result. Thus, quantifying and correcting these biases before the real survey begins is extremely important.

\begin{figure}
	\includegraphics[width=\columnwidth]{metacal_bias_shear_pplt.pdf}
    %\vspace*{-5mm}
    \caption{We show the recovered multiplicative bias on the shear as a function of applied shear for the choice of the applied shear in our \textcolor{red}{simplified} simulations. The presented multiplicative bias is the average of $m_{1}$ and $m_{2}$, and the grey shaded region represents the mission requirement. At first order, the \textsc{metacalibration} algorithm only works for small input shears. The next order effect is seen as a quadratic dependence of the multiplicative shear bias on on the applied shear (\citealt{2017ApJ...841...24S}). A larger input shear increases the signal-to-noise of bias estimates, but to keep the non-linear effect small compared to requirements, we limit input shears to $\pm 0.02$. }
    \label{fig:metacal_shear_linear}
\end{figure}

\subsection{\textsc{metacalibration} Formalism}
Here, we briefly summarize how \textsc{metacalibration} (\citealt{2017arXiv170202600H, 2017ApJ...841...24S}) calibrates the biased measurement of galaxy ellipticities on the image stamps. \textcolor{red}{Each stamp is defined to be an image cutout with one galaxy.} \textsc{metacalibration} creates one unsheared and four artificially-sheared galaxy stamps. Each is deconvolved with the input PSF, left unsheared or sheared with an additional gravitational shear of $\delta g=\pm 0.01$ in the two basis directions ($g_1$, $g_2$) and re-convolved with a new slightly larger isotropic, Gaussian PSF. \textcolor{red}{We have adopted to use the Gaussian PSF since it resembles the process in the current surveys and it requires complex operations to use a non-Gaussian PSF for the space-based survey. This choice could imply that we potentially isotropize the shapes of galaxies.} \textsc{metacalibration} works under the assumption that the input shear is small, otherwise the recovered shear would be biased without accounting for higher order terms. It is a balance to choose an input shear that results in higher S/N of the estimated shear bias  and unbiased shear measurement. Figure \ref{fig:metacal_shear_linear} shows the performance as a function of input shear leading to the choice of input shear $g=\pm 0.02$.

After processing the images with \textsc{metacalibration} and measuring the shapes with \texttt{ngmix}, we have 5 shape catalogs for the five values of shear applied by \textsc{metacalibration}. We can then compute the shear response from these catalogs and calculate the calibrated ensemble galaxy shears. The shear response can be understood as the change in objects' ellipticities with respect to the change in gravitational shear. Mathematically, the observed ellipticities, $\vb*{e}$ = ($e_{1}$, $e_{2}$), can be approximated using a Taylor expansion around the two-component shear, $\vb*{g}=0$. Higher terms here can be dropped assuming the gravitational shear is small: 
\begin{equation}
    \vb*{e} = \vb*{e}\rvert_{\vb*{g}=0} + \frac{\partial \vb*{e}}{\partial \vb*{g}}\bigg\rvert_{\vb*{g}=0}\vb*{g} + \ldots
\end{equation}
From this expression, the shear response matrix can be defined as 
\begin{equation}
    \vb*{R} \equiv \frac{\partial \vb*{e}}{\partial \vb*{g}}\bigg\rvert_{\vb*{g}=0} = 
    \begin{pmatrix}
        \partial e_{1}/\partial g_{1} & \partial e_{2}/\partial g_{1} \\ 
        \partial e_{1}/\partial g_{2} & \partial e_{2}/\partial g_{2}
    \end{pmatrix}. 
\end{equation}
The ensemble mean of measured ellipticities $\langle\vb*{e}\rangle$ can then computed. Since we expect galaxies to be randomly oriented such that $\langle\vb*{e}\rangle\rvert_{\vb*{g}=0}=0$, we have a relationship between the measured ellipticities and the input shear in the simulations, 
\begin{equation}
    \langle\vb*{e}\rangle \approx \langle \vb*{R}\rangle\langle\vb*{g} \rangle. 
\end{equation}
